On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fully define geometric units [31]

Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass and the speed of light are set to unity (i.e. $M=c=1$).

>>>>

Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass, the speed of light and the gravitational constant are set to unity (i.e. $M=c=G=1$).
